\section{Model Description}
\label{Model_Description}
The model consists of to processes. One for the economic production process and one for social learning about investment decisions amongst heterogeneous households.

\subsection{Economic production}
\label{model_description}

Economic production takes place in two sectors. For convenience, they will be called the \textit{clean} and the \textit{dirty} sector. The dirty sector uses labor $L$, dirty capital $K_d$ and a fossil resource $R$ as input factors, the clean sector uses labor $L$, clean capital $K_c$ and a renewable technology stock $C$ as input factors. It is assumed that the physical capital of one sector cannot be used in the other sector due to different technologies. We also assume that capital labor and knowledge are mutual substitutes but that the additional resource cannot be substituted. To satisfy these requirements, we use the following production functions:
\begin{equation}
	Y_c = b_c L_c^{\alpha_c}K_c^{\beta_c}C^{\gamma_c}, 
	\label{clean_production}
\end{equation}
in the clean sector, where $b_c$ is the Solow residual in the clean sector and $\alpha_c$, $\beta_c$ and $\gamma_c$ are the elasticities of the respective input factors and
\begin{equation}
	Y_d = {\rm min}\left( b_d L_d^{\alpha_d}K_d^{\beta_d}, e R \right),
	\label{dirty_production}
\end{equation}
in the dirty sector, where $b_d$ is the Solow residual in the dirty sector, $\alpha_d$ and $\beta_d$ are the input factors of the respective input factors and $e$ is the conversion efficiency of the fossil resource.
Additionally, it is assumed that
\begin{itemize}
	\item the usage of the fossil resource $R$ depletes geological resource stock $G$:
		\begin{equation}
			\dot{G} = -R, \quad G(t=0) = G_0
			\label{resource_depletion}
		\end{equation}
	\item the cost for the usage of the fossil resource depends on the resource use $R$ and the fraction of the remaining fossil resource stock $G/G_0$:
		\begin{equation}
			c_R = b_R R^{\rho}\left( \frac{G}{G_0} \right)^{\mu}
			\label{resource cost}
		\end{equation}
	\item perfect labor mobility and competition for labor between the two sectors, leading to an equilibrium wage that equals the marginal return for labor:
		\begin{equation}
			w = \frac{\partial Y_c}{\partial L_c} = \frac{\partial Y_d}{\partial L_d} - \frac{\partial c_R}{\partial L_d}
			\label{equilibrium_wage}
		\end{equation}
	\item technology specific capital, that can only be used in the sector that it has initially been invested in, leading to independent capital return rates for the two kinds of capital:
		\begin{align}
			r_c &= \frac{\partial Y_c}{\partial K_c} \\
			r_d &= \frac{\partial Y_d}{\partial K_d} - \frac{\partial c_R}{\partial K_d}
		\end{align}
	\item learning by doing with a chance of forgetting in the clean sector, leading to change in the renewable technology stock $C$:
		\begin{equation}
			\dot{C} = Y_c - \chi C
			\label{learning_by_doing}
		\end{equation}
\end{itemize}

\subsection{Investment Decision Making}

The model assumes $N$ heterogeneous households denoted with the index $i$ as owners of labor $L^{(i)}$ and capital $K_c^{(i)}$ and $K_d^{(i)}$ in (potentially) both economic sectors.
From this, households generate income
\begin{equation}
	I^{(i)} = w L^{(i)} + r_c K_c^{(i)} + r_d K_d^{(i)}
	\label{household_income}
\end{equation}
which they use for consumption $C^{(i)} = (1-s) I^{(i)}$ and savings $S^{(i)} = s I^{(i)}$. Households decision about where to invest their savings $o_i \in [c,d]$ about in which sector to invest their savings is the result of a social learning process closely adapted from the adaptive voter model:

Households form the nodes of a graph of acquaintance relations. Households get active at a constant rate. When a household $i$ becomes active, it interacts with one of its acquaintances $j$ chosen at random. If they hold the same opinion, nothing happens. If they hold different opinions, one of two things can happen:
\begin{itemize}
	\item Adaptation: with probability $\varphi$, the households end their relation and household $i$ connects to another household $k$, that holds the same opinion. 
	\item Imitation: with probability $1-\varphi$, an imitation event takes place and household $i$ assumes the opinion of household $j$ with probability $p_{ji}$ increasing with their difference in income.
\end{itemize}
The imitation probability is given as a monotonously increasing function of the difference in consumption between the two households:
\begin{equation}
	p_{ji} = \frac{1}{2}(1 + \tanh \left( C^{(j)} - C^{(i)}  \right)
	\label{imitation_probability}
\end{equation}
A fraction $\varepsilon$ of events are random, e.g. rewiring to a random other household or adopting a random new savings rate equally distributed between 0 and 1.

Given the savings decisions of the individual households, the time development of their capital holdings is given by

\begin{align}
	\dot{K}_c^{(i)} =& \delta_{o_i, c} \left( r_c K_c^{(i)} + r_d K_d^{(i)} + w L_i \right) - \kappa K_c \\
	\dot{K}_d^{(i)} =& \delta_{o_i, d} \left( r_c K_c^{(i)} + r_d K_d^{(i)} + w L_i \right) - \kappa K_d 
\end{align}

Assuming equal capital depreciation rates $\kappa$ in both sectors.
